---
title: "TRECC IVR Usage Analyses"
author: "Evelyn Yarzebinski, Benjamin Zinszer, Mackenzie Campbell"
output:
  html_document:
  toc: true
---

##0. Metadata
```{r prep data, include = F}
#clean up environment
rm(list=ls())
gc(verbose=TRUE)

source("TRECC_dataPrep.R")
```

###Report Generation Time
```{r report time, echo = F}
message(paste0("report generated: ",Sys.time()))

```

###What is the min/max and span of the data?
####Note: Date shown here is the most recent day in the dataset. Due to the time of data export from metabase, the most recent day will most likely not be a full, complete day.
```{r date range, echo = F}
UAS_maxDate = max(CIVdata_filter$date)
UAS_minDate = min(CIVdata_filter$date)
CDR_maxDate = max(cdrData_filter_IVRCall$date)
CDR_minDate = min(cdrData_filter_IVRCall$date)
UAS_nDays = UAS_maxDate - UAS_minDate + 1
CDR_nDays = CDR_maxDate - CDR_minDate + 1
message(paste("User Answer Data ranges from ", UAS_minDate," to ", UAS_maxDate,". The span is ",UAS_nDays," days.", sep = ""))
message(paste("CDR data ranges from ", CDR_minDate, " to ", CDR_maxDate,". The span is ",CDR_nDays," days.", sep = ""))
```

```{r saving, include=F}
write.csv(CIVdata_filter,paste("~/Documents/IvoryCoast/data/CIVData_currentDataThrough_",UAS_maxDate,".csv",sep=""),row.names = FALSE)
#write.xlsx(CIVdata_filter,paste("~/Documents/IvoryCoast/data/CIVData_currentDataThrough_",UAS_maxDate,".xlsx",sep=""),row.names = FALSE)
#write.csv(cdrData_filter,paste0("~/Documents/IvoryCoast/data/cdrData_currentDataThrough_",CDR_maxDate,".csv"),row.names = FALSE)
#write.xlsx(cdrData_filter,paste("~/Documents/IvoryCoast/data/cdrData_currentDataThrough_",CDR_maxDate,".xlsx",sep=""),row.names = FALSE)
```

##1. Explore the data
```{r student unit performance table, echo = F}
#perfomance per student per unit
Qcount_unit = CIVdata_filter %>%
  group_by(studentStudyId, UAS.unit_id) %>%
  summarize(uniqueQuestions = n_distinct(cmsQuestions.question_text),
            maxQuestionsPerUnit = max(questionNumberPerUnit),
            daysCalledIVR = n_distinct(date),
            avgCorrectnessOfQuestionAttempts = round(mean(UAS.correct),2))

Qcount_unit_currentUnit = Qcount_unit %>%
  group_by(studentStudyId) %>%
  summarize(currentUnit = max(UAS.unit_id))

datatable(Qcount_unit)

```

###Plot of student current progress in unit
####The scatterplot hows the units that each student is currently in (eg the "1" is unit 1). A student with a red dot has passed the threshold for promotion (50% mastery on 16+ questions) and will receive the next unit's content on their next call. A student with a grey dot is below the threshold for promotion and will receive the current unit's content the next time they call.
####To see student progress in the highest unit, sort the "Explore the data" table by UAS.unit_id (descending)

####{.tabset}
#####Scatterplot
```{r plot of current progress, echo = F}
Qcount_unit_filter <- Qcount_unit %>%
  ungroup() %>%
  mutate(readyForPromotion = ifelse(uniqueQuestions >= 16 & avgCorrectnessOfQuestionAttempts >= 0.50, "1", "0")) %>%
  mutate(currentUnit = ifelse(studentStudyId != lead(studentStudyId), 1, 0))

Qcount_unit_filter[nrow(Qcount_unit_filter), c("currentUnit")] <- 1

Qcount_unit_filter = Qcount_unit_filter %>%
         filter(currentUnit == 1)

ggplot(data=Qcount_unit_filter,aes(x=uniqueQuestions,y=avgCorrectnessOfQuestionAttempts,col = readyForPromotion)) + 
  geom_point() +
  facet_wrap(~ UAS.unit_id, ncol = 4) +
  scale_color_manual(values=c("grey56","red3"))
```

#####Unit Summary Table
```{r overall unit progress, echo = F}
overallUnit = Qcount_unit %>%
  group_by(studentStudyId) %>%
  summarize(currentUnit = max(UAS.unit_id))
  
overallUnit = overallUnit %>%
  group_by(currentUnit) %>%
  summarize(nUsers = n_distinct(studentStudyId))

datatable(overallUnit)
```

#####Student List
```{r student list, echo = F}
Qcount_unit_filter = Qcount_unit_filter %>%
  select(studentStudyId, UAS.unit_id)
datatable(Qcount_unit_filter)

#write.table(Qcount_unit_filter, "Qcount_unit_filter.csv", row.names = F, quote = F)
```

<!-- ###Student progress per unit per day -->
<!-- ####This table also includes the number of unique questions (not number of attempts of each question) that a student experienced.  -->
```{r student question performance per unit per day table, echo = F}
#questions and performance per student per unit per day
Qcount_day = CIVdata_filter %>%
  group_by(studentStudyId, UAS.unit_id,date) %>%
  summarize(uniqueQuestions = n_distinct(cmsQuestions.question_text),
            uniqueLessons = n_distinct(UAS.lesson_id),
            avgAttemptOfCorrectAnswer = round(mean(attemptNumber),2),
            sdAttemptOfCorrectAnswer = round(sd(attemptNumber),2),
            avgCorrectnessOfQuestionAttempts = round(mean(UAS.correct),2))

#datatable(Qcount_day)
```

##2. Usage Exploratory Analyses

###Usage patterns for each user (y axis) by each date (x axis)
#####The color of each point indicates the max unit a student encounters on a given day. If a student works on unit 1 and unit 2 on the same day, the point will be coded 'unit 2'.
#####Each point on the graph is a day that the student called the IVR. Each student has a horizontal line that connects that student's dots together. The line stops when a student stops calling.

####{.tabset}

#####Number of unique users per day
```{r users per day, echo = F}
#users per day
#usersPerDay = CIVdata_filter %>%
usersPerDay = CIVdata_filter %>%
  group_by(date) %>%
  summarize(uniqueUsers = n_distinct(studentStudyId))

#datatable(Qcount_usersPerDay)

ggplot(usersPerDay, aes (date,uniqueUsers))+
  geom_col()

```

#####Specific Students Using IVR
```{r user usage scatterplot, echo = F}
Qcount_day$UAS.unit_id = as.character(Qcount_day$UAS.unit_id)

ggplot(data=Qcount_day,aes(x=date,y=studentStudyId,group=studentStudyId, color=UAS.unit_id)) + 
  geom_path() +
  geom_point() +
  scale_color_manual(values=c("gray50","olivedrab3","darkgoldenrod1","firebrick1"))
#+
#  scale_color_manual(values=c("darkslategray","darkslategray4","darkslategray3","darkslategray2"))

```


###How much time do they spend on an average lesson?

####Note: Time is still approximate at the moment. I took (time of current line - time of previous line) only if the two lines' lesson ID and date was the same, and if the hour in which the attempt occurred was either the same hour as the previous attempt or h+1 (to account for a student doing a lesson across the hour threshold). This eliminates inflated values due to multiple calls throughout a day.

```{r avg time per lesson, echo = F}
AvgTimeLesson = CIVdata_filter %>%
  filter(!is.na(elapsedTimeSec)) %>%
  group_by(studentStudyId,UAS.lesson_id) %>%
    summarize(MinPerLesson = round(sum(elapsedTimeSec/60),2))

AvgTimeLesson_Agg = AvgTimeLesson %>%
  group_by(studentStudyId) %>%
  summarize(uniqueLessons = n_distinct(UAS.lesson_id),
            Avg_MinPerLesson = round(mean(MinPerLesson),2),
            SD_MinPerLesson = round(sd(MinPerLesson),2))

datatable(AvgTimeLesson_Agg)
```

***
***


<!-- ###Total number of days each user has called the IVR -->
<!-- ```{r days per user} -->
<!-- #how many users per day -->
<!-- daysPerUser = CIVdata_filter %>% -->
<!--   group_by(studentStudyId) %>% -->
<!--   summarize(totalDays = n_distinct(date)) -->

<!-- datatable(daysPerUser) -->
<!-- ``` -->

<!-- ###Total number of unique days a student has called since the deployment. -->

<!-- ```{r total days used} -->
<!-- #total days used -->
<!-- overallTotalDaysCalled = daysPerUser %>% -->
<!--   group_by(totalDays) %>% -->
<!--   summarize(countOfStudents = n_distinct(studentStudyId)) -->

<!-- datatable(overallTotalDaysCalled) -->
<!-- ``` -->
###When do students start calls, based on the CDR table?
####During April and May 2018 interviews with Michael and Amy, parents said that the ideal time for the IVR call was between 17h - 19h, after the children are home from school, eaten dinner, and finished their chores. We see that most of the calls come during this time, but a number of calls come in the morning and afternoon as well!
####The single histogram indicates - across all study days - the raw hour of the day when the IVR calls the student (based on Michel's IVR CDR call logs)
####The multiple histograms indicate - per each study day - the raw hour of the day when the IVR calls the student (based on Michel's IVR CDR call logs). Phone training on 10/24 was a Wednesday. Since there are 7 graphs in each row, this means that the first column of graphs represents each Wednesday in a given week. Columns 4 and 5 represent all Saturdays and Sundays, respectively.
###{.tabset}

####Single histogram (one across all study days)
```{r new lesson, hour of day - overall, echo = F}
callStart <- cdrData_filter_IVRCall
#callStart <- CIVdata_filter

ggplot(callStart, aes(x = hourExtract)) +
  geom_histogram(binwidth = 1)
```

####Multiple histograms (one per each study day)
```{r new lesson, hour of day - aggregate, echo = F}
callStart %>%
  ggplot(aes(x = hourExtract)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~ date, ncol = 7) 
```

###Avg Call Time Per User (updated with Michel's IVR CDR call logs)
####The table notes the total number of calls per student, total days, and average length of those calls.
####The scatterplot shows each unique student's number of calls (x axis) by average length of call (y axis).

###{.tabset}
####Table
```{r avg call time per user, echo = F}

#avgCallTime <- cdrData_filter %>%
#  left_join(Qcount_unit_currentUnit, by = c("studentStudyId")) %>%
  #mutate(extraLine = ifelse(studentStudyId == lead(studentStudyId) & callstart == lead(callstart), 1, 0)) %>%
  #filter(extraLine == 0) %>%
avgCallTime = cdrData_filter_IVRCall %>%
  group_by(studentStudyId) %>%
  summarize(nCalls = sum(inMichelsList),
            nDaysCalled = n_distinct(date),
            avgMinPerCall = round(mean(billsec)/60,2),
            sdMinPerCall = round(sd(billsec)/60,2))

datatable(avgCallTime)
```


####Scatterplot
```{r, echo = F}
avgCallTime %>%
  ggplot(aes(x = nCalls, y = avgMinPerCall)) +
  geom_point()
  #geom_jitter(alpha = .2, width = .2)
  #facet_wrap(~ questionAndUnit_concat, ncol = 5) +
  #stat_smooth()
```


<!-- ##3. Promotion Analysis -->

<!-- ###Question Progress For Promotion -->
<!-- ####This analysis is only for students who were promoted into subsequent units based on their performance. Students who never passed Unit 1 are excluded from this analysis. -->

<!-- ####How many questions did a student have to answer in the PRIOR unit until they achieved a high enough mastery score that allowed them to go to the next unit? You can read the table as "To be promoted into Unit 2, 12 students answered an average of 89 unique questions in Unit 1, ranging from a minimum of 15 to a maximum of 272." Or, "To be promoted into Unit 3, 8 students answered an average of 133 questions in Unit 2." -->

<!-- ###{.tabset} -->

<!-- ####Aggregate Table -->
<!-- ```{r, echo = F} -->
<!-- promotionQuestions = Qcount_unit %>% -->
<!--   filter(studentStudyId != 15, studentStudyId != 33, studentStudyId != 38) %>% -->
<!--   mutate(questionsAnsweredForPromotion = ifelse(studentStudyId == lag(studentStudyId), lag(uniqueQuestions),NA)) %>% -->
<!--   filter(UAS.unit_id != 1) -->

<!-- promotionQuestions_table = promotionQuestions %>% -->
<!--   group_by(UAS.unit_id) %>% -->
<!--   summarize(nStudentsPromoted = n_distinct(studentStudyId), -->
<!--             avgQ_ForPromotionToCurrentUnit = round(mean(questionsAnsweredForPromotion),2), -->
<!--             sdQ_ForPromotionToCurrentUnit = round(sd(questionsAnsweredForPromotion),2), -->
<!--             minQ_ForPromotionToCurrentUnit = min(questionsAnsweredForPromotion), -->
<!--             maxQ_ForPromotionToCurrentUnit = max(questionsAnsweredForPromotion)) -->

<!-- datatable(promotionQuestions_table) -->
<!-- ``` -->

<!-- ####Scatterplot -->
<!-- ```{r, echo = F} -->
<!-- promotionQuestions$UAS.unit_id = as.character(promotionQuestions$UAS.unit_id) -->

<!-- promotionQuestions %>% -->
<!--   ggplot(aes(x=daysCalledIVR,y=questionsAnsweredForPromotion, color=UAS.unit_id)) +  -->
<!--   geom_point() + -->
<!--   scale_color_manual(values=c("olivedrab3","darkgoldenrod1","firebrick1")) -->

<!-- ``` -->

<!-- ####Student Table -->
<!-- ```{r, echo = F} -->
<!-- datatable(promotionQuestions) -->

<!-- ``` -->

<!-- <!-- # ```{r, include = F} --> -->
<!-- # promotionQuestions_csv = promotionQuestions %>% -->
<!-- #   select(studentStudyId, UAS.unit_id) -->
<!-- #  -->
<!-- # write.csv(promotionQuestions_csv, "promotionStudents.csv", row.names = F) -->
<!-- # ``` -->
